### 2017-04-04 paper/evaluation.tex
done with RQ4.1

To evaluate the support of parallel execution of test suites, we
considered the \numMedLong{} projects that ran in at least one minute
identified in Section~\ref{sec:rqA} (\ie, \medg{} and \longg{}
groups). We are interested to know if developers consider low-level
parallelism features to amortize the execution cost. More precisely,
we investigate if there are projects with parallelism configuration
enabled by default or if developers configure this feature to run only
on specific scenarios (\eg, dedicated server).  We describe our
approach as follows:

@@

We configured Maven to output all configuration variables.  The
rationale is that, for each project's module, we can capture relevant
configurations and classify their parallelization level (see Section
\ref{sec:modes}) based on their values. To avoid waiting all tests to
terminate, we just run the bootstrap phase and we skip the actual test
execution.  According to Maven's
documentation~\cite{maven-surefire-plugin}, any parallelization
setting depends either on (1) \CodeIn{parallel} to define the
parallelism mode within a JVM followed by \CodeIn{threadCount} or (2)
\CodeIn{forkCount} (or \CodeIn{forkMode} in older versions) to define
the number of forked JVMs. For each test execution, we look for theses
parameters and their values to map to one of the possible
parallelization modes.  For instance, if a given project contains a
module with the setting \CodeIn{<forkCount>1C</forkCount>}, the
possible classifications are \ForkSeq{} or \ForkParMeth{} depending on
the presence and the value of the parameter \CodeIn{parallel}.
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our final results. Finally, some projects use a value
informed as an argument instead of adding the value statically in the
configuration value. In this case, we consider all possible values for
the parameterized parameter.  From the \numMedLong{} projects, we
identified \numProjectsPar{} projects with parallel execution enabled
by default.  Figure~\ref{tab:freqmodes-dynamic} summarizes our
findings.

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}llll}
        \toprule
        Group & Subject & - & -\\%
        \midrule%
        long   & JenkinsCI gerrit-trigger-plugin & 1 & \ForkSeq{}\\%
        medium & Jcabi & 1 & \ParClassParMeth{}\\%
        medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        medium & Apache logging-log4J2 & 25 & \ForkSeq{}\\%
        medium & Javaslang & 3 & \ParClassParMeth{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{\Fix{TODO}}
    \label{tab:freqmodes-dynamic}
\end{figure}

\Fix{Elaborate findings....}

@@

>>>>

To evaluate the support of parallel execution of test suites, we
considered the \numMedLong{} projects that ran in at least one minute
identified in Section~\ref{sec:rqA} (\ie, \medg{} and \longg{}
groups). We are interested to know if developers consider low-level
parallelism modes to amortize the execution cost (see
Section~\ref{sec:modes}). More precisely, we investigate if there are
projects with parallelization modes enabled by default or if
developers configure this feature to run only on specific scenarios
(\eg, dedicated server).  We describe our approach as follows:

@@

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.  From the
Maven output, we capture the parameters related to parallelism
configurations and mapped these configurations to a parallelization
mode.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.  From the \numMedLong{} projects, we
identified \numProjectsPar{} projects with parallel execution enabled
by default.  Figure~\ref{tab:freqmodes-dynamic} summarizes our
findings.

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        medium & Javaslang & 3 & \ParClassParMeth{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with test execution in parallel enabled by
    default}
    \label{tab:freqmodes-dynamic}
\end{figure}

@@

Finally, some projects use a value informed as an argument in the
command line instead of declaring a static value in the configuration
file (\ie, \pomf{}). In this case, we consider all valid values for
the parameter.
